%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Chief Technology Officer} % Job title
    {Scenario.com} % Organization
    {Paris, San Francisco} % Location
    {July 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-Founded Scenario.com, a platform that leverages Generative AI to assist indie developers, medium and large studios in effortlessly creating stunning, custom game assets with speed and artistic consistency.}
        \item {Primary responsibilities: Product Management, Product Owner, Technology Lead, Machine Learning Researcher, Platform architecture, Front, API, Cloud and ML Engineers management.}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Reached 2500+ daily active users,}
          \item {Enabled training and serving of 100k+ custom models,}
          \item {Generated dozens millions of images,}
          \item {Recognized as the Generative AI platform offering the best consistency.}
        \end{cvsubitems}
        \item {Lessons learned:}
        \begin{cvsubitems}
          \item {Never giving up, resiliency is key to success,}
          \item {Technology innovation reached new highs.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Startup Solutions Architect} % Job title
    {Amazon Web Services} % Organization
    {Paris} % Location
    {May 2019 - July 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Support onboarding and growth of startups on Amazon Web Services (AWS), definition of the early stage market strategy.}
        \item {Primary responsibilities: customer best interest, CTO in residence, Content Creation, Trainings, Public speaking.}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Helped 400+ startups grow on AWS,}
          \item {Set the EMEA Activate Onboarding sessions and its associated early startup journey, 1000+ startup onboarded,}
          \item {Dozen of public speaking, workshops and immersion days sessions leading,}
          \item {Blog posts, immersion day and workshops content creation,}
          \item {Initiate a major and peculiar partnership between AWS and a Startup.}
        \end{cvsubitems}
        \item {Lessons learned:}
        \begin{cvsubitems}
          \item {Amazon culture,}
          \item {Embrassing cloud has a strong tendancy to accelerate startup growth.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Director of Engineering} % Job title
    {Delair} % Organization
    {Paris, Toulouse} % Location
    {Oct. 2018 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Help merged the Airware assets into the Delair's platform.}
        \item {Primary responsibilities: Product Management, Data Science and Machine Learning integration, Engineers management.}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Support all former Airware's customers,}
          \item {Perpetuate the Redbird product.}
        \end{cvsubitems}
        \item {Lessons learned: Re-inventing the wheel is a business killer.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Director of Engineering, then CTO} % Job title
    {Airware} % Organization
    {Paris, San Francisco} % Location
    {Sep. 2016 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Support the transformation of a French startup into a global company.}
        \item {Primary responsibilities: Product Management, Data Science and Machine Learning Roadmap management, Platform architecture, Engineers management.}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Machine Learning workloads operating in production,}
          \item {Architecture principles defined with Redbird leveraged at the global level.}
        \end{cvsubitems}
        \item {Lessons learned:}
        \begin{cvsubitems}
          \item {Machine Learning applications are more than ample. We have just scratched the surface of their capabilities,}
          \item {Cloud-native services empower development teams to do more with less.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Vice President of Engineering, Acting CTO} % Job title
    {Redbird} % Organization
    {Paris} % Location
    {Jan. 2016 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Transform an MVP into a viable and scalable product, developing advanced partnerships and features.}
        \item {Primary responsibilities: Turning business vision into actionable technical strategy, Product Management, Partnership \& 3rd parties modules development, AWS team training} % from traditional databases and workloads to cloud-native services
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Working highly-available and fault tolerant architecture,}
          \item {Airware Acquisition Due Diligence,}
          \item {AWS Selection at the Startup Corner for Paris Summit.}
        \end{cvsubitems}
        \item {Lessons learned:}
        \begin{cvsubitems}
          \item {Startups ecosystem fits me like a glove,}
          \item {Working with cutting-edge technologies thrills me,}
          \item {Finding my way off the beaten paths wakes me up in the morning.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Manager, Innovation Program lead for Resource France} % Job title
    {Accenture} % Organization
    {Paris Area} % Location
    {Jul. 2015 - Jan. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Transformation program definition: spreading innovation through the Resources France group, including training selection,}
          \item {People acculturation and Network animation,}
          \item {``Paris Innovation Hub": offering definition, built a 20+ opportunities pipeline,}
          \item {Screened 10+ startups for future Accenture deals partnerships.}
        \end{cvsubitems}
        \item {Lessons learned: Train and experienced UX design, design thinking, lean startup, business model canvas.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Manager, Program Lead} % Job title
    {Accenture, for GRTgaz} % Organization
    {Paris Area} % Location
    {May 2012 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scope: 10+ applications in best of breed technologies, 60+ FTE on average (120+ max), 2 delivery centers,}
        \item {Features: Capacities Booking, Pricing, Measure, Allocation, Metering, CRM, Billing \& Invoicing, Gas Quality Analysis \& Simulation, Publication \& Alerting.}
        \item {Primary responsibilities: Program Management and Application Delivery, Finances and Risj management, Quality assurance.}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Transition from a set of different sub-contractors to local developments, near-shore (Nantes) and offshore (Mumbai, India),}
          \item {AWS cloud implementation: development and staging environments,}
          \item {20000+ man.days, hundreds of releases, 98\%+ green SLAs, while maintaing net margin.}
        \end{cvsubitems}
        \item {Lessons learned:}
        \begin{cvsubitems}
          \item {Managing large teams in different offices --- including delivery centers on different time zones, different languages,}
          \item {Public Cloud is disruptive, enables new use cases, unleashes creativity. With a major drawback: requires additional and strong cost controls.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant, Solution Architect} % Job title
    {Accenture, for GDF Suez} % Organization
    {Paris Area} % Location
    {Nov. 2009 - Sep. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Primary responsibilities: Studying and cross department solution design, Architectures and Roadmaps definitions, scenario sizing and scheduling.}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Architecture weighing document exposed at company council for the replacement of SAP and Selligent with Salesforce,}
          \item {Application design for energy consumption and optimization B2C system,}
          \item {Architecture scenarios definition (different budgets, schedules, and impacts on the ecosystem).}
        \end{cvsubitems}
        \item {Lessons learned: diplomacy is part of architecting solutions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant, System Analyst for GDF Suez team} % Job title
    {Accenture, for GDF Suez} % Organization
    {Paris Area} % Location
    {Jan. 2009 - Sep. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scope: SAP IS-U / CRM Utilities information system. 10 million customers, 3 thousand users, 40 million bills a year.}
        \item {Primary responsibilities: high-level business requirements gathering, general design, detailed solution design, sizing.}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Numerous features delivery: Price determination, CRM, Machine-Machine Interfaces, Meter Reading \& Integration orchestrator, Consumption Extrapolation, Billing and Invoicing, Budget Billing Plan Subscription, Dunning,}
          \item {Automatic Invoice validation tool development,}
          \item {Utilities industry vulgarization and Accenture Resource team training.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Analyst} % Job title
    {Accenture, for Gaz De France} % Organization
    {Paris Area} % Location
    {Jan. 2007 - Dec. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scope: SAP IS-U / CRM Utilities information system. 10 million customers, 3 thousand users, 40 million bills a year.}
        \item {Primary responsibilities: Functional and Technical requirements analyze, Solution design and costs analysis.}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Multiple application designs and implementations related to machine-machine interfaces, pricing, billing and invoicing,}
          \item {Maintenance of production workloads, emergency solving,}
          \item {Monitoring \& support of 60+ interfaces,}
          \item {Business expertise acquisition.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web developer} % Job title
    {Arcorp, Idoine, Satis (Web agency and software editor)} % Organization
    {Paris} % Location
    {Sep. 2005 - Dec. 2005} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web application development for the FSE (Fonds Social Européen).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
