%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activities}

%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Manager @ Accenture} % Job title
    {Intrapreuneurship experience: Video \& Image Analysis as a Service} % Organization
    {Paris Area} % Location
    {Dec. 2013 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Business plan definition: Accenture provides a sclable infrastructure used by drone operators and service providers,}
        \item {Platform UX prototyping. Proof of Concept development: data processing using GPU is possible in the cloud, the product can scale.}
        \item {Lessons learned: innovation thrills me and never doing the same thing is key to me. I do love to deal with new technology.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {iOS Developer} % Job title
    {Purring Box (Mobile Application)} % Organization
    {Paris Area} % Location
    {Jan. 2009 - Dec. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Product definition, design, development and deployment of a mobile application levraging purring therapy.}
        \item {Lessons learned: it can be easy to learn a new eco-system; getting an application from unknown to famous is the piece de resistance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teacher Assistant (20 tutors / 300 students), Web developer} % Job title
    {EPITA} % Organization
    {Paris} % Location
    {Jan. 2006 - Aug. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In charge of practical courses and lectures (Object Oriented Languages, Scripting, Design \& Design Pattersn, Unix).}
        \item {Internationalization of a social web site that manages ideas and initiatives development related to ecology and environment saving.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
